HaPy \\ Haskell for Python

### 2011-12-17 paper.tex
outline of paper
expanded outline

% IMPORTANT: BECAUSE WE ARE USING MINTED, YOU MUST SAY pdflatex -shell-escape paper.tex

\documentclass[11pt, letterpaper, oneside] {article}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fullpage}
\usepackage{minted}

\begin{document}
\parindent = 0cm

@@

\section{Further work}
In future, HaPy could support dynamic conversion from GADTs to Python types when instance of user-defined Haskell data are passed from the Haskell layer to the Python layer---in particular, Haskell's product types would map to Python classes while Haskell's sum types could be represented in Python by an enumerated type. 
\section{Refernces}
System.Plugins stuff.

Testing minted.
\begin{minted}{haskell}
fib :: [Int]
fib = 1 : 1 : foldWith (+) fib (tail fib)
\end{minted}
\end{document}

>>>>

\documentclass[11pt, letterpaper, oneside, twocolumn] {article}
\usepackage{minted}

\begin{document}

\title{HaPy \\
Haskell for Python
}
\author{David Fisher, Ashwin Siripurapu, and William Rowan}
\maketitle

\section{Introduction}

@@

\section{Use}

\subsection{Loading Haskell Modules}

\subsection{Haskell types in Python}

\section{Implementation}

\subsection{Dynamic Loading of Haskell modules}

\subsection{Function Currying}

\subsection{Type checking}

\section{Future work}
In future, HaPy could support dynamic conversion from GADTs to Python types when instance of user-defined Haskell data are passed from the Haskell layer to the Python layer---in particular, Haskell's product types would map to Python classes while Haskell's sum types could be represented in Python by an enumerated type.

\section{Refernces}
System.Plugins stuff.

\end{document}
